---
title: "Diamon Dataset ِAnalysis"
author: "Ebtisam alghamdi"
output: html_document
---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo = FALSE, character(length = 2),
                      message = FALSE, warning = FALSE)
```


```{r}
#Importing Packages That We Need 
library(tidyverse)
library(knitr)
library(ggplot2)
library(RColorBrewer)
library(kableExtra)
```


```{r}

#Reading The Diamonds Dataset 
diamonds <- read.csv("diamonds.csv")
```


In this report i will do some analysis on __"Diamonds"__ dataset.The [dataset](https://www.kaggle.com/shivam2503/diamonds) contain diamonds attributes like _carat,cut,color,clarity,depth and price_.

This report will answer many quastions like :

* what is the range of the diamonds price?o
* which attribute will effect the diamond price ?
* What is highest diamond price and its attributes?o
* what is the diamonds colors and which has the highest value and price ?
* What is the different names of the diamonds clarity?
* what is the attributes for each diamonds cut?

This Dataset contain 53940 different Diamonds type with price range :


```{r}
#What is the range of the diamonds prices?

kbl(diamonds %>%
  summarise(The_Range=range(diamonds$price)))

```

```{r}
#Show the diamonds prices in relation with the carat 
ggplot(diamonds, aes(x = carat, y = price,color=cut)) +
  geom_point(Shape= 16, alpha=0.4)+
  theme_classic()
```



__Diamonds Prices With Relation with Carat__

#What is highest diamond price and its attributes?

```{r}

#The Highest Diamond Price 
diamonds %>% 
  filter(price== max(price))

```

