---
title: "Nutritional Facts For Most Common Foods"
output: html_document
---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo = FALSE, character(length = 2),
                      message = FALSE, warning = FALSE)

library(tidyverse)
library(knitr)
library(DT)
library(munsell)
library(RColorBrewer)
library(ggplot2)
```

Nowadays, everybody is mindful of what they eat. Counting calories and reducing fat intake is the number one advice given by all dietitians and nutritionists. Therefore, we need to know which foods are rich in which nutrients, __Don't we?__

__What are the research question that you are trying to answer with this data set?__

*The Calories Range for each Food Cateogry?o
*The highest food with Portein?o
*The highest food with Fat?
*Which vegetable contain high Faber?  



The [dataset](https://www.kaggle.com/niharika41298/nutrition-details-for-most-common-foods) contains more than _300_ foods each with the amount of Calories, Fats, Proteins, Saturated Fats, Carbohydrates, Fibers labeled for each food. Also, the foods are categorized into various groups:

* Dairy products
* Fats, Oils, Shortenings
* Meat, Poultry
* Fish, Seafood
* Breads,cereals,fast food,grains
* Desserts
* Vegetables
* Fruits 

```{r}

#Reading our Dataset:

nfc <- read_csv("Nfacts.csv")
```

```{r}
#Supset from dataset 

nfcs<-nfc[,c("Calories","Fat","Carbs")]
```

```{r}


# Clean up the data

# Remove , in numbers
# str_replace(nfc$Calories, ",", "")

# remove - in numbers
# str_replace(nfc$Calories, "-", "")

# convert to numeric
# as.numeric(nfc$Calories)


nfc <- nfc %>% 
  mutate(Calories = str_replace(Calories, ",", ""),
         Calories = str_replace(Calories, "-", ""),
         Calories = as.numeric(Calories))

# Remove t in (fat, portin, sat.fat,fiber,carbs) replace it with "0"
# convert (fat,portin and sat.fat) to numeric 

nfc <- nfc %>% 
     mutate(Fat= str_replace(Fat,"t","0"),
            Fat= as.numeric(Fat))


nfc <- nfc %>% 
  mutate(Protein= str_replace(Protein, "t", "0"),
         Protein= as.numeric(Protein))


nfc <- nfc %>% 
  mutate(Sat.Fat= str_replace(Sat.Fat, "t", "0"),
         Sat.Fat= as.numeric(Sat.Fat))

nfc <- nfc %>% 
  mutate(Fiber= str_replace(Fiber, "t", "0"),
         Fiber= as.numeric(Fiber))

nfc <- nfc %>% 
  mutate(Crabs= str_replace(Carbs, "t", "0"),
         Carbs= as.numeric(Carbs))

# Remove "A-E , F-P , R-Z" form Vegetables an Fruits Catogery names 

nfc <- nfc %>% 
  
  mutate(Category= str_replace(Category, "Vegetables A-E", "Vegetables"),
         Category= str_replace(Category, "Vegetables F-P", "Vegetables"),
         Category= str_replace(Category, "Vegetables R-Z", "Vegetables"),
         Category= str_replace(Category, "Fruits A-F", "Fruits"),
         Category= str_replace(Category, "Fruits G-P", "Fruits"),
         Category= str_replace(Category, "Fruits R-Z", "Fruits"))
       


```


#Table Of Nutrition Facts Classified by -Category- :

```{r}
nfc %>% 
  datatable(options = list(dom = 'Blfrtip',
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All")))
  )
```



```{r echo=FALSE}

#The Calories Range for each Cateogry?

 ggplot(nfc,aes(x=Calories,y=Category,color=Category))+
geom_point(shape=16,alpha=0.4)+
 scale_y_continuous(limits=c(0,335))+
  theme_classic()
```

```{r}
#The Highest Food With Protein 
nfc[which(nfc$Protein==max(nfc$Protein)),c("Food","Category","Protein")]



```

```
